---
title: "Untitled"
output:
  pdf_document: default
  html_document: default
---

# After the attacking from the virus

## Analysis of the confirmed people

- Figure out which kind of people are the most vulnerable to this COVID19
- Divide the age variables into several intervals

```{r echo=FALSE, warning=TRUE}
a = read.csv('PatientInfo.csv')


library("survival")
library("survminer")
data('lung')
library('coin')
library('party')


a = a[1:794,]
age = as.numeric(unlist(strsplit(as.character(a$age), split = 's')))
D = data.frame(date = a$confirmed_date, status = rep(1, nrow(a)))

D$date = as.Date(as.character(D$date))
D$date = D$date - D$date[1]
D$age = cut(age, breaks = c(0, 40, 50, 60, 70, 80, Inf))
D$sex = factor(as.character(a$sex))
```
The prepared dataset is following:
```{r}
head(D)
```


- We consider the comfirmed cases.
- log-rank test for different groups of people.
- The p value is smaller than 0.05, which means that there is differences in these groups.

## Log-rank test

```{r}
D = D[complete.cases(D),]

fit = survfit(Surv(date, status) ~ sex + age, data = D)
summary(fit)$table
ggsurvplot(fit, data = D, pval = TRUE)
```


- Visualization of cumulative function of different group people.

```{r echo=FALSE}
ggsurv <- ggsurvplot(fit, fun = "event", conf.int = TRUE,
                     ggtheme = theme_bw())

## Get the different plots for these events
ggsurv$plot +theme_bw() + 
  theme (legend.position = "right")+
  facet_grid(age~sex)
```

## Cox model

- For exact comparison of the risk to be affected by the CVOD of different groups, Cox model is a good choice.

- From the cox model, we can see that there is one significant people within certain age interval suffers significant risk from other people.

```{r echo=FALSE}
fit.coxph <- coxph(Surv(time, status) ~ sex + age, 
                   data = D)
summary(fit.coxph)
ggforest(fit.coxph, data = D)

```


- Model checking about the cox model fitness.
- The martingale residuals seems that they have 0 means, indicating that overall the model fits the data reasonably well.
```{r echo=FALSE}


layout(matrix(1:2, ncol = 2))
 res <- residuals(fit.coxph)
 plot(res ~ age, data = D, ylim = c(-2.5, 1.5),
         pch = ".", ylab = "Martingale Residuals")
 abline(h = 0, lty = 3)
 plot(res ~ sex, data = D, ylim = c(-2.5, 1.5),
         pch = ".", ylab = "")
 abline(h = 0, lty = 3)


```



# God bless our nation. Rid us of mutation.
## Thank You
